---
title: "exam2_sim"
author: "Tianchu Ye"
date: "December 9, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Setup

For more accurate result, each simulation will run for 10000 (nsim) times. The self-defined function is to calculate the mode of sets.\

```{r}
rm(list = ls())
options(warn=-1) 
nsim <- 10000
mode <- function(list){
  myhist <- hist.default(list,plot = FALSE)
  return(myhist$breaks[which.max(myhist$density)+1])} 
```

# Drugs
```{r}
price = 3.7; OnetimeCost = 16; CapCost = 0.4; ProdCost = 0.2; t = 10
```

##1.
Below is the simulation for the problem. The **suggested capacity level is 50K.**\

```{r}
capacity <- c(30,35,40,45,50,55,60)*1000
ExpProfit <- matrix(ncol = length(capacity), nrow = nsim)
for (r in 1:nsim){
  profit <- rep(0,length(capacity))
  demand <- round(rnorm(t,50000,12000))
  for (i in 1:length(capacity)){
    my_capacity <- capacity[i]
    produce <- min(c(demand[1],my_capacity))
    profit_ <- produce*(price - ProdCost) - my_capacity*(OnetimeCost+CapCost) 
    for (j in 2:t){
      produce <- min(c(demand[j],my_capacity))
      profit_ <- profit_+ produce*(price - ProdCost) - my_capacity*CapCost}
    profit[i] <- profit_
    ExpProfit[r,i] <- profit_}
}
MeanExpProfit <- c()
for (i in 1:length(capacity)){
  MeanExpProfit[i] <- mean(ExpProfit[,i])}
maximized <- capacity[which.max(MeanExpProfit)]
paste("The suggested capacity level is",maximized)
```
The Plot:\
```{r}
plot(capacity,MeanExpProfit,main = "Capacity vs 10-year Profit")
abline(v = maximized,lty = 2)
```
##2.
Here, I ran another set of simulation with the chosen capacity level and the confidential interval of 95% is printed out in the end.\

```{r}
totalProfit <- rep(0,nsim)
for (r in 1:nsim){
  demand <- round(rnorm(t,50000,12000))
  produce <- min(c(demand[1],maximized))
  profit_ <- produce *(price - ProdCost) - maximized*(CapCost + OnetimeCost)
  for (j in 2:t){
      produce <- min(c(demand[j],maximized))
      profit_ <- profit_+ produce*(price - ProdCost) -  maximized*CapCost}
  totalProfit[r] = profit_}
#The 95% condifential interval for profit is:
(quantile(totalProfit,c(0.025,0.975)))
```

# Warranty

```{r}
device_cost = 100; t2 = 6
```

**The Simulation(s)**

```{r}
numOwned <- c(); Paid <- c()
for (r in 1:nsim){
  PaidDevice = 1 ; nsamp = 50 
  brokeTime <- rgamma(nsamp,2,0.5)
  for (t in 1:nsamp){
    if(sum(brokeTime[1:t])>=t2){break}}
  myTime <- brokeTime[1:t]; PaidDevice = length(myTime[myTime>1])
  numOwned[r] <- t; Paid[r] <- PaidDevice}
```

##3.
```{r}
CostPlot <- Paid * device_cost
# round mean cost to nearest 100 due to integer device number
myCost <- round(mean(CostPlot)/device_cost)*device_cost 
paste("My total cost is", myCost)
```
##4.
```{r}
inWarrantyPlot <- round(numOwned-Paid)
inWarranty <- round(mean(inWarrantyPlot))
paste("Number of failures during the warranty period is",inWarranty)
```

##5.
```{r}
MeanOwned <- round(mean(numOwned))
paste("Number of devices owned during 6-year period is", MeanOwned)
```
Plots for Question 3,4,5:\
```{r}
par(mfrow = c(3,1))
hist(CostPlot,main = "Total Cost")
hist(inWarrantyPlot,main = "Failures in Warranty period (1 yr)");
hist(numOwned,main = "Owned Device(s)")
par(mfrow = c(1,1))
```

# Clearance
##6.
```{r}
Day <- rep(0,nsim);n_samp <- 100
for (r in 1:nsim){
Arrivals <- sample(x=0:4, size=n_samp, prob=c(.15,.25,.3,.2,.1), replace=TRUE)
#Given Information
pNotbuy <- 1-.6 #denoted as 0
pTop <- 0.6*0.4 #denoted as 1
pRegular <- .6*.35  #denoted as 2
pExtra <- .6*.25  #denoted as 3
machineAmounts <- c(5,4,3)
#Generate Demand for each coming customer
Demand <- sample(x = 0:3, size = n_samp,prob = c(pNotbuy,pTop,pRegular,pExtra),
                 replace = TRUE)
#"-1" denotes that the customer actually buys a machine;
#"0" means no demand or desired machine is sold out.
for (nppl in 1:n_samp){
  if (sum(machineAmounts) == 0){break}
  for (c in 1:3){if (Demand[nppl] == c){
      if(machineAmounts[c]>0)
        {Demand[nppl] <- -1; machineAmounts[c]<- machineAmounts[c]-1}
      else{Demand[nppl] =0}}}}
for(day in 1:n_samp){if(sum(Arrivals[1:day])>=nppl){break}}
Day[r] <- day}
hist(Day,main = "Selling Days",breaks = 30) #larger breaks for more details
```
The histogram shows that the distribution is skewed to right. Therefore, the result is chosen as the mode value of set "Day" using self-defined function mode() in set-up section.\
**My answer:**
```{r}
result3 <- mode(Day)
paste("It will take WTF", result3,"days to sell all 12 washers (mode chosen).")
paste("The mean value for Selling Days is rounded as",round(mean(Day)))
```

#Waiting Room

##7.
$$SampleMean = \frac{\Sigma sample}{n}$$
$$Sample S.D = \sqrt{\frac{\Sigma(t-\bar{t})^2}{n-1}}$$

```{r}
SampleTime <- c(8,12,26,10,23,21,16,22,18,17,36,9)
paste("The sample mean is", round(mean(SampleTime),digits = 2))
a <- sum((SampleTime - mean(SampleTime))^2)/(length(SampleTime)-1)
paste("The sample standard deviation is", round(sqrt(a),digits = 2))
```
##8.
The confidence interval is: 
$$ \bar{x} \pm \frac{c\times s}{\sqrt{n}}$$
After calculation, my answer is:
$$18.17 \pm 7.27 = [-4.17,10.38]$$
```{r,include=FALSE}
c = qt(.995,df = 12-1)
num = c*sqrt(a)/sqrt(12)
(c-num); (c+num)
```

##9.
SUggested sample size is:
$$ n = \frac{c_{99\%}^2\times s^2}{E^2} \approx 79$$
```{r,include=FALSE}
round(c^2*a/(8))
```

# Scenarios
##10. 
Use time series to predict the trends and then pick the top ones.


#MultiChoice
##11. c) Heteroscedasticity

##12. c) density plot

##13. b) lag

##14. c) B(500,0.08)

##15. c) pbinom(50,500,.08,lower.tail = F)

##16. d) 40

##17. d) 7

# *1693 Corp.*

##18.
Approximately 2%.\
```{r}
round(pnorm(460,mean = 480, sd = 10,lower.tail = T),digits = 2)
```

##19.
$$\mu_{2X} = \mu_1 + \mu_2 = 920 grams$$
$$\sigma_{2X} = \sqrt{\sigma_1^2+\sigma_2^2 + 2\cdot\sigma\cdot \sigma_1 \cdot_2 CORR(X_1,X_2)} \approx 18.81grams$$
```{r,include = F}
sqrt(10^2+10^2+2*10*10*0.77)
```

##20.
$$2X = N(920,18.81)$$
$$P(2X < 920) = 0.5$$
The probability is 50%.\
```{r,include = F}
round(pnorm(960,mean = 960, sd = 18.81,lower.tail = T),digits = 2)
```
##21.
The suggested $\mu$ is 477.
```{r}
for (mu in 450:500){
if(pnorm(460,mu,10,lower.tail = FALSE) >= .95){break}}
mu
```
