---
title: "RidgeRegression"
author: "Group 2-07"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting up

packages needed: "leaps", "ISLR"(for data), "glmnet" (for regression models)
```{r}
options(warn=-1)   # Supress warning messages
installIfAbsentAndLoad <- function(neededVector) {
  for(thispackage in neededVector) {
    if( ! require(thispackage, character.only = T) )
    { install.packages(thispackage)}
    require(thispackage, character.only = T)
  }
}

# class contains the knn() function, KNN contains the
# knn.reg() function, combinat contains the combn() function
needed <- c("leaps", "ISLR", "glmnet")  
installIfAbsentAndLoad(needed)
```
We will use the **glmnet** package in order to perform ridge regression and
the lasso. \
The main function in this package is *glmnet()*, which can be used to fit ridge regression models, lasso models, and more.\
This function has slightly different syntax from other model-fitting functions that we have encountered thus far in this book. In particular, we must pass in an $x$ matrix as well as a $y$ vector, and we do not use the $y \sim x$ syntax. We will now perform ridge regression and the lasso in order to predict Salary on the Hitters data.\
\
The *model.matrix()* function is particularly useful for creating $x$; not only does it produce a matrix corresponding to the 19 predictors but it also automatically transforms any qualitative variables into dummy variables.\
The latter property is important because *glmnet()* can only take numerical, quantitative inputs.
```{r}
Hitters <- na.omit(Hitters)
str(Hitters)
x <- model.matrix(Salary ~ ., Hitters)[, -1]     #We omit the intercept
y <- Hitters$Salary
#install.packages("glmnet")
```

## Ridge Regression
The **glmnet()** function has an $\alpha$ argument that determines what type of model is fit. If $\alpha=0$ then a ridge regression model is fit, and if $\alpha=1$ (the default) then a lasso model is fit. In this lab we want to fit a ridge regression model so we need to set it to 0.\
By default the *glmnet()* function performs ridge regression for an automatically selected range of lamda values. However, here we have chosen to implement the function over a grid of values ranging from $\lambda = 10^{10}$ to $\lambda = 10^{-2}$, essentially covering the full range of scenarios from the null model containing only the intercept, to the least squares fit. As we will see, we can also compute model fits for a particular value of $\lambda$ that is not one of the original grid values.\

Note that by default, the *glmnet()* function standardizes the variables so that they are on the same scale. To turn off this default setting, use the argument **standardize=FALSE**.\
Associated with each value of $\lambda$ is a vector of ridge regression coefficients, stored in a matrix that can be accessed by *coef()*. In this case, it is a $20\times100$ matrix, with 20 rows (19 predictors plus an intercept) and 100 columns (one for each value of $\lambda$).

Divide the interval from 10 to -2 into 100 partitions - make these the exponents of 10, so the *grid* vector goes from $10^{10}$ to 0.01 in 100 (diminishing) steps.
```{r glmnet}
grid <- 10 ^ seq(10, -2, length=100)  
ridge.mod <- glmnet(x,y,alpha=0,lambda=grid)
str(ridge.mod$beta)
dim(coef(ridge.mod))
```
We expect the coefficient estimates to be much smaller, in terms of l2 norm, when a large value of $\lambda$ is used, as compared to a small one.
```{r}
# These are the coefficients when lamda = 10,000,000,000, along with their l2 norm: 
ridge.mod$lambda[1]
coef(ridge.mod)[,1]
sqrt(sum(coef(ridge.mod)[-1,1]^2))
```
```{r}
# These are the coefficients when lamda = 11,498, along with their l2 norm: 
ridge.mod$lambda[50]
coef(ridge.mod)[,50]
sqrt(sum(coef(ridge.mod)[-1,50]^2))
```
Note the much larger l2 norm of the coefficients associated with the smaller value of $\lambda$.\
We can use the *predict()* function for a number of purposes. For instance, we can obtain the ridge regression coefficients for a new value of $\lambda$, say 50:
```{r}
predict(ridge.mod,s=50,type="coefficients")[1:20,]
```
We now split the samples into a training set and a test set in order to estimate the test error of ridge regression. 
```{r}
set.seed(1)
train <- sample(1:nrow(x), nrow(x)/2)
test <- (-train)
y.test <- y[test]
```
Next we fit a ridge regression model on the training set, and evaluate its MSE on the test set, using lamda = 4. 
```{r}
ridge.mod <- glmnet(x[train,],y[train],alpha=0,lambda=grid, thresh=1e-12)
ridge.pred <- predict(ridge.mod,s=4,newx=x[test,])
mean((ridge.pred-y.test)^2)
```
The test MSE is 101037. Note that if we had instead simply fit a model with just an intercept, we would have predicted each test observation using the mean of the training observations. In that case, we could compute the test set MSE like this:
```{r}
mean((mean(y[train])-y.test)^2)
# We could also get the same result by fitting a ridge regression model with
# a very large value of lamda. Note that 1e10 means 10^10.
ridge.pred <- predict(ridge.mod,s=1e10,newx=x[test,])
mean((ridge.pred-y.test)^2)
```
So fitting a ridge regression model with $\lambda$ = 4 leads to a much lower test MSE than fitting a model with just an intercept. We now check whether there is any benefit to performing ridge regression with $\lambda$ = 4 instead of just performing least squares regression. Recall that least squares is simply ridge regression with $\lambda$ = 0\


Note: In order for *glmnet()* to yield the exact least squares coefficients when $\lambda$ = 0, we use the argument *exact=TRUE* when calling the predict() function. Otherwise, the predict() function will interpolate over the grid of lamda values used in fitting the glmnet() model, yielding approximate results. When we use exact=T, there remains a slight discrepancy in the third decimal place between the output of glmnet() when $\lambda$ = 0 and the output of lm(); this is due to numerical approximation on the part of glmnet().\
```{r}
ridge.pred <- predict(ridge.mod,s=0,newx=x[test,],exact=T,x=x[train,],y=y[train])
mean((ridge.pred-y.test)^2)
lm(y~x, subset=train)
predict(ridge.mod,s=0,exact=T,type="coefficients",x=x[train,],y=y[train])[1:20,]
```
In general, if we want to fit a (unpenalized) least squares model, then we should use the lm() function, since that function provides more useful outputs, such as standard errors and p-values for the coefficients.\
Also, instead of arbitrarily choosing lamda = 4, it would be better to use cross-validation to choose the tuning parameter lamda. We can do this using the built-in cross-validation function, cv.glmnet(). By default, the function performs ten-fold cross-validation, though this can be changed using the argument nfolds. Note that we set a random seed first.
```{r}
set.seed(1)
cv.out <- cv.glmnet(x[train,],y[train],alpha=0)
plot(cv.out)
bestlam <- cv.out$lambda.min
bestlam
```
Therefore, we see that the value of $\lambda$ that results in the smallest cross validation error is 212. What is the test MSE associated with this value of $\lambda$?
```{r}
ridge.pred <- predict(ridge.mod,s=bestlam,newx=x[test,])
mean((ridge.pred-y.test)^2)
```
 This represents a further improvement over the test MSE that we got using $\lambda$ = 4. Finally, we refit our ridge regression model on the full data set, using the value of $\lambda$ chosen by cross-validation, and examine the coefficient estimates.
```{r}
out <- glmnet(x,y,alpha=0)
predict(out,type="coefficients",s=bestlam)[1:20,]
```
As expected, none of the coefficients are zero.\
Ridge regression does **not** perform variable selection!
